---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# densityLocPoly

<!-- badges: start -->
<!-- badges: end -->

This package is designed to estimate bivariate densities using nonparametric 
local polynomial procedures using data that belong to (complicated) domains.
Examples can be found in the subdirectory `examples/` of the package.

## Installation

You can install the development version of densityLocPoly from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
# devtools::install_github("klutchnikoff/densityLocPoly")
devtools::install_github("klutchnikoff/densityLocPoly", build_vignettes = TRUE)
```
## Getting started

```{r}
library("densityLocPoly")
```

## Examples 

Examples used in the companion paper ArXiV:yyXXXXXX are accessible as follows:
```{r eval=FALSE, include=TRUE}
vignette("example-sector", package = "densityLocPoly")
```








