---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# densityLocPoly

<!-- badges: start -->
<!-- badges: end -->

This package is designed to estimate bivariate densities using nonparametric 
local polynomial procedures using data that belong to (complicated) domains.
Examples can be found in the subdirectory `examples/` of the package.

## Installation

You can install the development version of densityLocPoly from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("klutchnikoff/densityLocPoly")
```
## Getting started

```{r}
library("tidyverse")
library("densityLocPoly")
```

## Examples 

## Comparison with `sparr`

```{r}
x <- dlstats::cran_stats(c("latticeDensity", "sparr"))

if (!is.null(x)) {
  ggplot(x, aes(end, downloads, group = package, color = package)) +
    geom_line() +
    geom_point() +
    scale_y_log10()
}
```

In the following example, we use the data 

```{r message=FALSE, warning=FALSE}
gather_LP <- TRUE # if TRUE we plot the boxplot of LP = min(LP0, LP1)

for (k0 in c(1, 2.1)) {
  for (type in c("poly", "norm")) {
    risk <- get(str_c("risk_", type))

    find_best_h <- risk |>
      group_by(h, method) |>
      summarise(mse = mean(value)) |>
      group_by(method, .drop = TRUE) |>
      summarise(h = h[which.min(mse)])

    bplot <- semi_join(risk, find_best_h, by = c("method", "h")) |>
      filter(k == k0) |>
      select(rep, n, method, value)

    # best LP
    if (gather_LP) {
      bplot <- bplot |>
        pivot_wider(names_from = method, values_from = value) |>
        (\(.){
          mutate(., LP = purrr::pmap_dbl(
            select(., contains("LP")),
            pmin,
            na.rm = TRUE
          ))
        })() |>
        select(n, SPARR, LP) |>
        pivot_longer(-n, names_to = "method")
    }

    ylimit <- bplot |>
      group_by(n, method) |>
      summarise(l = quantile(value, 0.75) + 1.59 * IQR(value))
    ylimit <- max(ylimit$l)

    print(
      ggplot(bplot) +
        aes(x = method, y = value, fill = method) +
        geom_boxplot(position = position_dodge(), outlier.shape = NA) +
        coord_cartesian(ylim = c(0, ylimit)) +
        xlab("") +
        facet_wrap(~n, nrow = 1) +
        scale_fill_grey(start = 0.5, end = 0.9) +
        theme_classic() +
        theme(
          legend.position = "none",
          axis.title.y = element_blank(),
          axis.line.y = element_blank()
        )
    )
  }
}
```




