---
title: "example-sector"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{example-sector}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  message = FALSE,
  warning = FALSE
)
options(mc.cores=2)
```

```{r setup}
library(densityLocPoly)
library(densityLocPoly)
library(spatstat)
library(tidyverse)
library(patchwork)
```

## Example densities

In the paper [1], four densities are used, two for each domain $\mathcal{D}_1$ and $\mathcal{D}_{2.1}$. Here, we represent these densities.

```{r}
K <- c(1, 2.1)
TYPE <- c("f_poly", "f_norm")

par(mar = c(0.1, 0.1, 1.1, 0.1))
for (k in K){
  domain <- polynomial_sector(k)
  for (f_type in TYPE) {
    f <- function(x, y) {do.call(f_type, list(x, y, k))}
    imf <- as.im(f, domain, dimyx = 512)
    plot(imf,
      col = grey(seq(1, 0.2, length = 256)),
      main = str_glue("density: {f_type} -- k: {k}"),
      ribbon=FALSE)
    plot(domain, add = TRUE)
    contour(imf, add = TRUE, nlevels = 12, lwd = 1, lty = 1)
  }
}
```

Notice that the functions f_poly() and f_norm() are defined in the package.

## Monte carlo simulations on the risk

The package provides the function `simulate_risk_polysec()` which allows to evaluate the risk (using Monte-Carlo replications – see the variable `RR`) of our estimation procedure on $n$-samples (where $n$ belongs to `NN`) simulated on several domain $\mathcal{D}_k$ (for $k$ in `KK`) for the two types of densities `f_poly()` and `f_norm()`. Notice that the estimation procedures are evaluate for different values of the bandwidth given in `HH`.

```{r}
risk_P <- simulate_risk_polysec(
  NN = c(500, 1000),
  RR = 1:10,
  HH = seq(0.01, 0.6, by = 0.02),
  KK = c(1, 2.1),
  density_type = "f_poly"
)

risk_N <- simulate_risk_polysec(
  NN = c(500, 1000),
  RR = 1:10,
  HH = seq(0.01, 0.6, by = 0.02),
  KK = c(1, 2.1),
  density_type = "f_norm"
)
```

Let’s take a look at the result.

```{r}
risk_P |> 
  filter(rep %in% 1:2)
```

Several method are used: LPm corresponds to our method where the degree of the local polynomial is set to $0$, $1$ or $2$. `SPARR` is the method implemented in the package `sparr`.

## Boxplot of the oracle estimator

```{r}
for (k0 in c(1, 2.1)) {
  for (type in c("P", "N")) {

    risk <- get(str_glue("risk_{type}"))

    find_best_h <- risk |>
      group_by(n, h, method) |>
      summarise(mse = mean(value)) |>
      group_by(n, method, .drop = TRUE) |>
      summarise(h = h[which.min(mse)], mse = min(mse))

    find_best_h <- bind_rows(
      # a
      find_best_h |>
      group_by(n) |>
      filter(str_detect(method, "^LP")) |>
      filter(mse == min(mse)),
      # b
      find_best_h |>
      filter(str_detect(method, "^SPARR"))
    ) |> select(n, method, h)

    bplot <- semi_join(risk, find_best_h, by = c("method", "h")) |>
      filter(k == k0) |>
      select(rep, n, method, value) |> 
      mutate(method = str_replace(method, "LP[0123456789]*", "LP"))

    ylimit <- bplot |>
      group_by(n, method) |>
      summarise(l = quantile(value, 0.75) + 1.59 * IQR(value)) |> 
      pull(l) |> 
      max()

    gg <- ggplot(bplot) +
      aes(x = method, y = value, fill = method) +
      geom_boxplot(
        position = position_dodge(),
        outlier.shape = NA
      ) +
      coord_cartesian(ylim = c(0, ylimit)) +
      stat_summary(fun = "mean") +
      xlab("") +
      ggtitle(str_glue("type: {type}     k = {k0}")) +
      facet_wrap(~n, nrow = 1) +
      scale_fill_grey(start = 0.5, end = 0.9) +
      theme_classic() +
      theme(
        legend.position = "none",
        axis.title.y = element_blank(),
        axis.line.y = element_blank()
      )
    print(gg)
  }
}

```

## More replications?

These graphs are obtained with only $10$ replications. We also provide data with $1,000$ replications. They can be easily obtained.

```{r}
risk_poly |> 
  filter(rep %in% 1:2)
```

```{r}
glimpse(risk_norm)
```

